Combining living and fossil taxa into phylogenies: the missing data issue

### 2014-11-30 Manuscript/TEM_draft.tex
Updated figures

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/BW/Global-ML+consensus-RF+Tr-small.pdf}
\caption{Trend of the effect of missing data on topological recovery on ML and consensus trees. The amount of missing data per parameter ($M_{L}$, $M_{F}$ and $M_{C}$) is represented along the x axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The topological recovery is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Maximum Likelihood trees are represented in black and the Bayesian consensus trees in grey.}
\label{Fig_Global-single}
\end{figure}
%Differences between the parameters and between the methods (ML vs BC)

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/BW/Global-Bootstrap+Treeset-RF+Tr-small.pdf}
\caption{Trend of the effect of missing data on topological recovery on ML and consensus trees. The amount of missing data per parameter ($M_{L}$, $M_{F}$ and $M_{C}$) is represented along the x axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The topological recovery is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Bootstrap trees pairwise comparisons are represented in black and the Bayesian posterior trees distribution pairwise comparisons in grey.}
\label{Fig_Global-treesets}
\end{figure}
%Differences between the parameters and between the methods (BS vs TS)

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/colour/Parameters-AllMethods-RF+Tr-small.pdf}
\caption{Comparison between the effect of missing data and the tree inference method on topological recovery. The amount of missing data for each parameter is represented on the x axis. The topological recovery is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Maximum Likelihood trees are represented in black, the Bayesian consensus trees in red, the bootstrap trees in green and the posterior tree distribution in blue.}
\label{Fig_Parameter-Method}
\end{figure}
%Differences within the parameters, not between

>>>>

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/colour/Parameters-AllMethods-RF+Tr-small.pdf}
\caption{Comparison between the effect of missing data and the tree inference method on topological recovery. The amount of missing data for each parameter is represented on the x axis. The topological recovery is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Maximum Likelihood trees are represented in black, the Bayesian consensus trees in red, the bootstrap trees in green and the posterior tree distribution in blue.}
\label{Fig_Results_1} %Differences within a subset of parameters and between methods
\end{figure}

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/BW/Global-ML+consensus-RF+Tr-small.pdf}
\caption{Trend of the effect of missing data on topological recovery on ML and consensus trees. The amount of missing data per parameter ($M_{L}$, $M_{F}$ and $M_{C}$) is represented along the x axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The topological recovery is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Maximum Likelihood trees are represented in black and the Bayesian consensus trees in grey.}
\label{Fig_Results_2} %Differences between all the parameters and between two methods (ML vs BC)
\end{figure}

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/colour/PairComp_within-Baycon-RF+Tr.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Bayesian consensus trees. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (BC=1) to red (BC=0). A. Results for the Normalised Robinson-Foulds distance. B. Results with the for Normalised Triplets distance.}
\label{Fig_Results_3}
\end{figure} %Pairwise BC for the Bayesian consensus trees for RF and TR. (parameters differences)

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/colour/PairComp_without-RF+Tr.pdf}
\caption{Distribution of the Bhattacharyya Coefficients between methods. Curves represents the kernel density estimations of the BC between the four different methods. A. Results for the Normalised Robinson-Foulds distance. B. Results with the for Normalised Triplets distance. Pikes around the two different extremes values of the BC show the two pairs of most dissimilar methods (Bayesian consensus vs. Bootstraps and Bayesian consensus vs. Bayesian tree posterior distribution) for the Normalised Robinson-Foulds distance ; and the most similar methods (Bootstraps and Bayesian tree posterior distribution) for the Normalised Triples methods.}
\label{Fig_Results_4} %Comparisons between methods, both in RF and Triplets.(method differences)
\end{figure}
